---
title: 'Prepare Data'
author: 
output: 
  github_document:
    toc: yes
editor_options: 
  chunk_output_type: console
---

```{r "setup", include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE,
                      fig.align = "center",
                      fig.path=('../../report/figures/'))
library(printr)
options(digits = 2)
library(rmarkdown)
```

# Scripts
- [Required Packages &amp; Reproducibility](#required-packages-&amp;-reproducibility)
- [Tidy Data](#tidy-data)
- [Save Data for Analysis](#save-data-for-analysis)
- [Visualization of Data](#visualization-of-data)
  - [Dependent Variable](#dependent-variable)
  - [Independent Variable](#independent-variable)
  - [Control Variables](#control-variables)
  - [Correlations Matrix](#correlations-matrix)

## Required Packages &amp; Reproducibility
```{r "env", message=FALSE, warning=F}
rm(list=ls())
renv::snapshot()
source(here::here("src/lib/functions.R"))
```

## Tidy Data
Load manually annotated data - for a validation excercise see [here](Calculate_ICR.R) for the code and [here](../../data/intermediate/Subset_data_intercode_reliability.csv) for the data - and create variables for being in opposition (`in_opposition`) and whether the party is a newly founded party (`new_party`).

```{r "get handcoded data"}
d <- read_csv(here("data/raw/coded-data-NL-2017-campaign.csv")) %>%
  mutate(id = paste(date, party, sep = "."))

table(d$date, d$party)
```

Not all parties are present at all days of the month, indicated by value `0` in the table.
We ensure that all days in the 2017 campaign period are present in our data, for the purpose of times-series cross-sectional analyses. 

```{r "mutate handcoded data"}
source(here("src/data-processing/mutate-handcoded-data.R"))
```

### Ideological Extremity: CHES and Manifesto Project
We have four ways to measure ideological extremity. 
We look at party's deviation from (a) the median party, and (b) the mean party, as measured by the [2017 Chapel Hill Expert Survey](https://www.chesdata.eu/2017-chapel-hill-expert-survey) and the [Manifesto Project](https://manifesto-project.wzb.eu/).

We first add the [2017 Chapel Hill Expert Survey](https://www.chesdata.eu/s/CHES_means_2017.csv) to our manually annotated data `d` to calculate party's ideological extremity for the 2017 (`ie_mean_ches2017` and `ie_median_ches2017`), and 2012 election campaigns (`ie_mean_ches2014` and `ie_median_ches2014`).


```{r "add ches data"}
source(here("src/data-processing/add-ches-data.R"))
```

Second, we added data from the [Manifesto Project](https://manifesto-project.wzb.eu) to our manually annotated data `d` to calculate party's ideological extremity based on the 2017 (`ie_mean_cmp2017` and `ie_median_cmp2017`), and 2012 election manifesto's (`ie_mean_cmp2012` and `ie_median_cmp2012`) as well as to add the seat share of the party in the national elections most prior to 2017 (`seats`).

```{r "add mp data"}
source(here("src/data-processing/add-mp-data.R"))
```

### Standing in the Polls
Subsequently, we add [polling data](https://nl.wikipedia.org/wiki/Tweede_Kamerverkiezingen_2017/Peilingen) to our manually annotated data.
We calculate the relative gains (or losses) based on: a) polled seats vis-a-vis parliamentary seats prior to the 2017 elections (`poll_standing1`),  b) lagged polled seats by 1 day vis-a-vis parliamentary seats prior to the 2017 elections (`poll_standing2`), c) lagged polled seats by 1 week vis-a-vis parliamentary seats prior to the 2017 elections (`poll_standing3`), d) polled seats vis-a-vis lagged polled seats by 1 day (`poll_standing4`), e) polled seats vis-a-vis lagged polled seats by 1 week (`poll_standing5`), f) lagged polled seats by 1 day vis-a-vis lagged polled seats by 1 week (`poll_standing6`).

```{r "add polls data"}
source(here("src/data-processing/add-polls-data.R"))
```

### Associative Issue Ownership
We use the October 2016 panel wave of KiesKompas to measure associative and competence issue ownership.
We measure associative issue ownership with the question _Which issue comes to your mind when you think about <party>?_.
For each question, associative issue ownership variables will be measured by summation over the respondents and calculating in percentages how many of the respondents associate an issue with a party.

```{r "add KK data-1"}
source(here("src/data-processing/add-KiesKompas-data1.R"))
```

# Competence Issue Ownership
We use the October 2016 panel wave of KiesKompas to measure competence issue ownership.
We measure competence issue ownership with the question _do you agree or disagree with <party> on the issue you associated with the party?_.
For each question, the compentence issue ownership variables will be measured by summation over the respondents.
Negative figures imply that more people disagree with the position of the party than people have agreed with the position of the party.

```{r "add KK data-2"}
source(here("src/data-processing/add-KiesKompas-data2.R"))
```

## Save Data for Analysis
```{r "save data"}
save(d, file = here("data/intermediate/cleaned_data.RData"))
```

## Visualization of Data

```{r "Overview of Appeals per Medium", echo=F, message=FALSE, warning=FALSE, fig.width=6, fig.height=8}
d %>%
  select(party, source, medium,direction_appeal) %>%
  group_by(party) %>% mutate(n = n()) %>%
  ungroup() %>%
  filter(direction_appeal != "No Appeal") %>%
  group_by(party, source, medium,direction_appeal, n) %>%
  summarise(tot = n(),
            perc = round(tot/n,2)) %>%
  mutate(id = paste(party, source, direction_appeal, tot),
         source = ifelse(medium=="Facebook", "Facebook", source),
         medium = ifelse(medium=="Facebook", "Social Media", medium),
         medium = factor(medium, 
                         levels = c("Newspapers", "TV-shows", "Social Media"))) %>%
  distinct(id, .keep_all = T) %>%
  ggplot(mapping = aes(x = party, y = perc, fill = source)) +
  facet_grid(rows = vars(medium),
             cols = vars(direction_appeal), space = "free", 
             scales = "free_y") +
  geom_col(alpha = .8, position = position_dodge()) +
  labs(x = "", y = "") +
  theme_minimal() +
  scale_y_continuous(labels=percent) +
  scale_fill_viridis_d() +
  theme(plot.title = element_text(hjust = 0.5),
        legend.position="bottom",
        legend.title = element_blank()) +
  guides(fill=guide_legend(nrow=2, byrow=T)) +
  coord_flip()
```

### Dependent Variable

```{r "Dependent Variable", echo=F}
d %>%
  select(direction_appeal, party) %>%
  filter(direction_appeal != "No Appeal") %>%
  group_by(direction_appeal, party) %>%
  summarise(n = n()) %>%
  ungroup() %>% group_by(party) %>%
  mutate(perc = round(n/sum(n),2)) %>%
  ggplot(mapping = aes(x = party, y = perc, fill = direction_appeal)) +
  geom_col(alpha = .8, position = position_dodge()) +
  labs(y = "", x = "", title = "Appeals made by Parties") +
  theme_minimal() +
  scale_y_continuous(labels=percent) +
  scale_fill_viridis_d() +
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(angle=45),
        legend.position="bottom",
        legend.title = element_blank()) 
```

### Independent Variable
```{r "Independent Variables - JI", echo=F, message=FALSE, warning=FALSE}
d %>%
  filter(direction_appeal != "No Appeal") %>%
  select(journalistic_intervenience,party) %>%
  group_by(journalistic_intervenience, party) %>%
  summarise(n = n()) %>%
  ungroup() %>% group_by(party) %>%
  mutate(perc = round(n/sum(n),2),
         journalistic_intervenience = recode(journalistic_intervenience,
         `0` = "No Journalistic Intervenience (Facebook)",
         `0.5` = "Medium Journalistic Intervenience (TV-shows)",
         `1` = "Strong Journalistic Intervenience (Newspapers)"),
         journalistic_intervenience = factor(journalistic_intervenience,
                                             levels = c("No Journalistic Intervenience (Facebook)", "Medium Journalistic Intervenience (TV-shows)", "Strong Journalistic Intervenience (Newspapers)"))) %>%
  ggplot(mapping = aes(y = perc, x = party, 
                       fill = journalistic_intervenience)) +
  geom_col(alpha = .8, position = position_dodge()) +
  labs(y = "Appeals", x = "", title = "Journalistic Intervenience (H1a)") +
  theme_minimal() +
  scale_fill_viridis_d() +
  scale_y_continuous(labels=percent) +
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(angle=45),
        legend.position="bottom",
        legend.title = element_blank()) +
  guides(fill=guide_legend(nrow=3,byrow=TRUE))
```


```{r "Independent Variables - Polls", echo=F, message=FALSE, warning=FALSE}
d %>%
  filter(direction_appeal != "No Appeal") %>%
  select(party, poll_standing1:poll_standing9) %>%
  distinct(party, .keep_all = T) %>%
  pivot_longer(cols = poll_standing1:poll_standing9,
               names_to = "id",
               values_to = "polls") %>%
  drop_na() %>%
  mutate(id = recode(id, 
                     `poll_standing1` = "Polls (Measure 1)",
                     `poll_standing2` = "Polls (Measure 2)",
                     `poll_standing3` = "Polls (Measure 3)",
                     `poll_standing4` = "Polls (Measure 4)",
                     `poll_standing5` = "Polls (Measure 5)",
                     `poll_standing6` = "Polls (Measure 6)",
                     `poll_standing7` = "Polls (Measure 7)",
                     `poll_standing8` = "Polls (Measure 8)",
                     `poll_standing9` = "Polls (Measure 9)")) %>%
  ggplot(mapping = aes(y = polls, x = party, colour = id)) +
  geom_point(position = position_dodge(width = 0.80), size = 2) +
  labs(y = "", x = "", title = "Standing in the Polls (H1b)") +
  theme_minimal() +
  scale_color_viridis_d() +
  scale_y_continuous(labels=percent) +
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(angle=45),
        legend.position="bottom",
        legend.title = element_blank()) +
    guides(color=guide_legend(nrow=3,byrow=TRUE))
```

```{r "Independent Variables - IO", echo=F, message=FALSE, warning=FALSE,fig.width=10, fig.height=10}
d %>%
  filter(direction_appeal != "No Appeal") %>%
  select(party, issue, aio_percentage, cio_mean:cio_sd) %>%
  drop_na() %>%
  pivot_longer(cols = aio_percentage:cio_sd,
               names_to = "id",
               values_to = "io") %>%
  mutate(id = recode(id,
                     `aio_percentage` = "Associative Issue Ownership: Percentage",
                     `cio_mean` = "Competence Issue Ownership: Mean Value",
                     `cio_median` = "Competence Issue Ownership: Median Value",
                     `cio_sd` = "Competence Issue Ownership: Standard Deviation")) %>%
  ggplot(mapping = aes(y = io, x = party, 
                       color = id)) +
  facet_wrap(.~issue, ncol = 4) +
  geom_point(position = position_dodge(width = 0.80), size = 2) +
  labs(y = "", x = "", title = "Issue Ownership (H2a)") +
  theme_minimal() +
  scale_color_viridis_d() +
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(angle=45),
        legend.position="bottom",
        legend.title = element_blank())  +
  guides(color=guide_legend(nrow=2,byrow=TRUE))
```


```{r "Independent Variables - IE", echo=F, message=FALSE, warning=FALSE,fig.width=10, fig.height=7}
d %>%
  filter(direction_appeal != "No Appeal") %>%
  select(party,ie_median_ches2017:ie_median_cmp2012) %>%
  mutate(ie_mean_cmp2017 = ie_mean_cmp2017/10,
         ie_median_cmp2017 = ie_median_cmp2017/10,
         ie_mean_cmp2012 = ie_mean_cmp2012/10,
         ie_median_cmp2012 = ie_median_cmp2012/10,) %>%
  drop_na() %>%
  distinct(party, .keep_all = T) %>%
  pivot_longer(cols = ie_median_ches2017:ie_median_cmp2012,
               names_to = "id",
               values_to = "extremity") %>%
  mutate(id = recode(id,
                     `ie_median_ches2017` = "Difference from Median (CHES 2017)",
                     `ie_mean_ches2017` = "Difference from Mean (CHES 2017)",
                     `ie_median_ches2014` = "Difference from Median (CHES 2014)",
                     `ie_mean_ches2014` = "Difference from Mean (CHES 2014)",
                     `ie_mean_cmp2017` = "Difference from Median (MP 2017)",
                     `ie_median_cmp2017` = "Difference from Mean (MP 2017)",
                     `ie_mean_cmp2012` = "Difference from Median (MP 2012)",
                     `ie_median_cmp2012` = "Difference from Mean (MP 2012)")) %>%
  ungroup %>%
  ggplot(mapping = aes(y = extremity, x = party, 
                       colour = id, group = id)) +
  geom_point(position = position_dodge(width = 0.80), size = 2) +
  labs(y = "", x = "", title = "Ideological Extremity (H2b)") +
  theme_minimal() +
  scale_color_viridis_d() +
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(angle=45),
        legend.position="bottom",
        legend.title = element_blank())  +
  guides(colour=guide_legend(nrow=4, byrow=T))
```

### Correlations Matrix
```{r "Correlations Matrix", echo=F, message=T, warning=T, fig.width=15, fig.height=15}
d %>%
  filter(direction_appeal != "No Appeal") %>%
  select(`Appeals made by Parties` = direction_appeal,
         `Journalistic Intervenience` = journalistic_intervenience,
         `Standing in the Polls (1)`  = poll_standing1,
         `Standing in the Polls (2)`  = poll_standing2,
         `Standing in the Polls (3)`  = poll_standing3,
         `Standing in the Polls (4)`  = poll_standing4,
         `Standing in the Polls (5)`  = poll_standing5,
         `Standing in the Polls (6)`  = poll_standing6,
         `Standing in the Polls (7)`  = poll_standing7,
         `Standing in the Polls (8)`  = poll_standing8,
         `Standing in the Polls (9)`  = poll_standing9,
         `Associative Issue Ownership`  = aio_percentage,
         `Competence Issue Ownership: Mean`  = cio_mean,
         `Competence Issue Ownership: Median`  = cio_median,
         `Competence Issue Ownership: Standard Deviation`  = cio_sd,
         `Ideological Extremity: Mean (CHES 2017)` = ie_mean_ches2017, 
         `Ideological Extremity: Median (CHES 2017)` = ie_median_ches2017,
         `Ideological Extremity: Mean (CHES 2014)` = ie_mean_ches2014,
         `Ideological Extremity: Median (CHES 2014)` = ie_median_ches2014,
         `Ideological Extremity: Mean (MP 2017)` = ie_mean_cmp2017,
         `Ideological Extremity: Median (MP 2017)` = ie_median_cmp2017,
         `Ideological Extremity: Mean (MP 2012)` = ie_mean_cmp2012,
         `Ideological Extremity: Median (MP 2012)` = ie_median_cmp2012,
         Source = source) %>%
  ggcorrmat(
  type = "robust", # correlation method
  cor.vars = c(everything()), # a range of variables can be selected
  colors = c("#440154FF", "#21908CFF", "#FDE725FF"),
  title = "Correlalogram for Variables under Study"
)
```
